---
title: "My First R Markdown"
author: "Christina Bergmann"
date: "January 17, 2017"
output: html_document
---

First, we want to set up our document and load all libaries.
```{r setup, include=FALSE}
#Do not show the code underlying the output in the final document
knitr::opts_chunk$set(echo = FALSE)

#Let's load some libraries we will need. If you notice later on that you need more libraries, add them here!
library(tidyverse)

#Make nice tables with the kable function
library(knitr)
```

```{r readdata, include=FALSE}
#Read in some fun comic character data
# via https://github.com/fivethirtyeight/data/tree/master/comic-characters
comic_data = read.csv("data/dc-wikia-data.csv.txt")

#I am going to remove some cases here where sex is not labelled

comic_data = comic_data[comic_data$SEX!="",]
```

The data we show is based on a 538 article entitled: "Comic Books Are Still Made By Men, For Men And About Men."
You can read it at: https://fivethirtyeight.com/features/women-in-comic-books/

Let's check what the data look like, in a nicely formatted table. Try removing the `kable` command and see what happens to your output.


```{r Info}
kable(head(comic_data))
```


Now some plots! I simply played around with some basic ggplot built-ins, try some other options (or visualizations based on data that you have processed a bit). 

```{r plot_1}
evil_woman = ggplot(comic_data, aes(x = SEX, y = ALIGN)) +
  geom_bin2d()

evil_woman
```



```{r plot_2}
evil_woman = ggplot(comic_data, aes(x = SEX, y = ALIGN)) +
  geom_count()

evil_woman
```


```{r chunktitle, eval=FALSE, echo = TRUE}
#This code is not supposed to work. R does not mind because here eval is set to FALSE
rg'vb;eroha'eogr\p
```

